---
title: "KOF Meta Information - Multi-Lingual Data Descriptions"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(kofdata)
```

The KOF API makes more than **500'000 time series about Swiss economy** available. 
Hence thorough **data descriptions** are very important. For the lion's share of the data, i.e., those time series stemming from the **business tendency surveys, meta descriptions** are available in **English, German, French and Italian**. You can use iso 2-digit country codes to display a series description in the desired language. 


```r
get_metadata("ch.kof.inu.ng08.fx.q_ql_ass_bs.balance","it")


# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance
# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$sa
# [1] "originale"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$item
# [1] "saldo (quota in %)"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$noga
# [1] "noga 2008"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$region
# [1] "Svizzera totale"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$sector
# [1] "settore totale (lettera nomenclatura generale delle attività economiche C # (ATTIVITÀ MANIFATTURIERE))"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$source
# [1] "KOF Centro di ricerche congiunturali"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$dataset
# [1] "inchiesta Industria"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$variable
# [1] "situazione degli affari, sentenza"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$variable_type
# [1] "domanda qualitativa con scala a 3 punti"

# $ch.kof.inu.ng08.fx.q_ql_ass_bs.balance$variable_period
# [1] "periodo totale"


```




### Some Swissness


On an endnote: {kofdata} is made in Switzerland and can return official two character abbreviations for all 26 cantons (states). 

```r
kofdata::cantons()
# [1] "AG" "AR" "AI" "BL" "BS" "BE" "FR" "GE" "GL" # "GR" "JU" "LU" "NE"
# [14] "NW" "OW" "SH" "SZ" "SO" "SG" "TG" "TI" # "UR" "VS" "VD" "ZG" "ZH"

```

