---
title: "{kofdata} data sources"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(kofdata)
```

## Public Collections


The KOF Data API exposes time series data and allows KOF partners and the broader 
public to consume data manually and in automated fashion. The following collections
of time series data are publicly available: 

- KOF Tourism Forecast Summer Season 
- KOF Tourism Forecast Winter Season
- KOF Tourism Forecast Year
- KOF Consensus Forecast
- KOF Globalization index 2018 vintage
- KOF Globalization index 2019 vintage
- KOF Main Indicators (KMI)
- KOF-Baublatt-Ausblick fitted values
- KOF-Baublatt-Ausblick Realtime
- KOF innovation survey (PAN) set for SBFI
- KOF Consensus Forecast Dates
- KOF Consensus Forecast Maximum
- KOF Consensus Forecast Mean
- KOF Consensus Forecast Minimum
- KOF Consensus Forecast Median
- KOF Consensus Forecast Probabilities
- KOF Consensus Forecast Standard Deviation
- [KOF Open Government Data Datasets](https://opendata.swiss/de/dataset?q=KOF)

Run `list_available_collections()` to find the name of a collection which you can use the reference to a particular collection. 


## KOF High Frequency Dashboard

In April 2020, KOF composed a list of alternative indicators for Switzerland that 
are available at a higher frequency than common economic indicators. These 
indicators were derived from publicly available data. Many of these indicators are updated until today and can be 
consumed throught the KOF Data REST API and the {kofdata} R package. To learn visit  [kofdata.netlify.app](https://kofdata.netlify.app)
